Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-15 paper/main.tex
Footnote fix

The benchmarking results for the \ac{SUPERCOP} toolkit of the \ac{SHA}-3
candidates and \ac{SHA}-2 functions on a number of different plattforms and
architectures are available at the webpage of eBACS
\footnote{\url{http://bench.cr.yp.to/results-sha3.html}}.

@@

\paragraph{Sphlib} is a C and Java library made by Thomas Pornin
\footnote{\url{http://www.saphir2.com/sphlib/}}, which contains all the second
round \ac{SHA}-3 candidates. Some of the same implementations are also found in
\ac{SUPERCOP}, while others, like the Cubehash implementation we have used is
not.

>>>>

The benchmarking results for the \ac{SUPERCOP} toolkit of the \ac{SHA}-3
candidates and \ac{SHA}-2 functions on a number of different plattforms and
architectures are available at the webpage of eBACS\footnote{\url{http://bench.cr.yp.to/results-sha3.html}}.

@@

\paragraph{Sphlib\protect\footnote{\url{http://www.saphir2.com/sphlib/}}}is a C and
Java library made by Thomas Pornin , which contains all the second round
\ac{SHA}-3 candidates. Some of the same implementations are also found in
\ac{SUPERCOP}, while others, like the Cubehash implementation we have used is
not.
